---
title: "Pilot Data Checklist"
author: "Guannan Shen (Risk Rejection: Allhands)"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, 
  output_dir = "../analysis_reports") })
output: 
  pdf_document: 
    toc: false
mainfont:: SourceSansPro
fontsize: 12pt
---

```{r setup, include=FALSE, cache = FALSE}
require("knitr")
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
opts_chunk$set(engine = "R")
knitr::opts_chunk$set(echo = F)
knitr::opts_chunk$set(message = F)
knitr::opts_chunk$set(warning = F)

opts_knit$set(root.dir = getwd())
                                                 
```


```{r libs}
## set up workspace
rm(list = ls())
library(tidyverse)
library(expss)
library(kableExtra)

# helper functions
source("./helper.R")
source("./data_clean_time.R")
source("./table_helper.R")
source("./missing_helper.R")
 # low-level grid functions are required
options(stringsAsFactors = F)
options(dplyr.width = Inf)

## not in function
'%nin%' <- Negate('%in%')

# ######## clean memory ######################
# rm(list = ls())
# gc()
# ls()
# slotNames(x)
# getSlots(x)

```


```{r data}
# the processed main dataset
data <- readRDS("../data/processing/data_labels.rds")
# useful cols collection
screening_cols <- c("PriorBreastCancer", "BreastRemoved", "ChestRad",
                    "DCIS-LCIS", "BRCA1/2", "CowdenSyn", "LiFraumeni")
# expected to be complete columns
complete_cols <- c("Experimental condition", "abs_risk_rounded", 
                   "abs_risk_pct", "abs_risk_lifetime_rounded",
                   "abs_risk_age_group_rounded", "abs_risk_age_group_pct",
                   "abs_risk_no_cancer_cohort", 
                   "abs_risk_age_group_no_cancer_cohort",
                   "50yr_absolute_risk",
                   "50yr_absolute_risk_lifetime",
                   "50yr_absolute_risk_age_group",
                   "50yr_RR_Star1", "50yr_RR_Star2", "50yr_abs_risk_rounded",
                   "50yr_abs_risk_pct", "50yr_abs_risk_lifetime_rounded",
                   "50yr_abs_risk_age_group_rounded", 
                   "50yr_abs_risk_age_group_pct", 
                   "50yr_abs_risk_no_cancer_cohort",
                   "abs_risk_relative_text",
                   "50yr_abs_risk_age_group_no_cancer_cohort")
# risk rejection related, better be complete
risk_rej_cols <- c("Q1", "Q2","Q3","Q4","Q5","Q6", "Q7")
# cross tabulation
conditions <- c("Experimental condition", "Pre-estimate")

# check both missingness and values 
# rename by column label
risk_comprehension <- c("Q1.11", "Q2.11")
risk_comp_label <- c("RComp1", "RComp2")

object_num <- c("Q1.12", "Q2.12", "Q3.11")
object_label <- c("ObjNum1", "ObjNum2", "ObjNum3")

# check related columns 
related_answers <- c("Q1.2", "Q1a", "Q2.2", "Q2a")


```


```{r targetingCol}
# Risk Comprehension and Objective Numeracy items (columns MP-MQ, NA-NC).
# excel_column_to_number("MP")
# data[,c(354, 355)]
# sapply(data[,c(354, 355)], var_lab)
# excel_column_to_number("NA")
# data[,c(365, 366, 367)]
# sapply(data[,c(365, 366, 367)], var_lab)
# 
# excel_column_to_number("DA")
# data[,c(105, 106)]
# data$Q1a
# excel_column_to_number("DG")
# data[,c(111, 112)]

```

# Data quality assurance checklist

## Screening

Participants who answer “yes” to any of the following questions 
(columns L-R) should not have any other data (**Checklist 3**).


```{r screening}
data <- data %>% create_screen_label(screening_cols)

dataNA <- data %>% filter(Pass_screening == "No")
summarize_missingness(dataNA, complete_cols) %>% 
  create_pdf_table(caption = 
                  "Check Missingness: Risks (Subjects do not pass screening)")
# risk rejection missing
summarize_missingness(dataNA, risk_rej_cols) %>% 
  create_pdf_table(caption = 
          "Check Missingness: Risk Rejections (Subjects do not pass screening)")
```


```{r subset}
data <- data %>% filter(Pass_screening == "Yes")
```

## After Screening

### Check Group Design 

Each category (1-3) should have approximately 30% of observations 
(**Checklist 1**). The key question `Pre-estimate` have answers in only 2 of 
the 3 experimental conditions, no answer for condition #3 (**Checklist 2**).


```{r grouping}
tab <- data %>% select(`Experimental condition`) %>% table(useNA = 'ifany')
tab %>% create_pdf_table(caption = 
                          "Check counts by experimental condition groups")
round(prop.table(tab), 2) %>% create_pdf_table(caption = 
                          "Check balanced grouping by experimental conditions")

# # just simple crosstabulation, base R 'table' function
tab <- data %>% select(all_of(conditions)) %>% table(useNA = 'ifany')

# Generate a table formatted for PDF using kableExtra
tab %>% create_pdf_table(caption = 
                "Cross-tabulation of Experimental Condition and Pre-estimate",
                    row_names = TRUE, label = TRUE)
```

### Check Missingness

All participants should have data in the following personal risk 
variables (**Checklist 4**), check missingness on risk rejection questions 
(**Checklist 5**).


```{r demonstration}
## roughly equal grouping 

# missingness
# risk missing
summarize_missingness(data, complete_cols) %>% 
  create_pdf_table(caption = "Check Missingness: Risks")
# risk rejection missing
# tab1 <- summarize_missingness(data, risk_rej_cols)
# row.names(tab1)

summarize_missingness(data, risk_rej_cols) %>% 
  create_pdf_table(caption = "Check Missingness: Risk Rejections")

```


### Check Related Columns

```{r related}
# # check related columns 
# related_answers <- c("Q1.2", "Q1a", "Q2.2", "Q2a")
# change column name by labels 
df1 <- generate_missingness_flag(data, "Q1a")

tab <- df1 %>% select(all_of(c("Q1.2", 
                                "missingness_Q1a"))) %>% 
                  table(useNA = 'ifany')
tab %>% create_pdf_table(caption = 
                "Cross-tabulation of Beliefs free response and Q1 answer",
                    row_names = TRUE, label = TRUE)

df2 <- generate_missingness_flag(data, "Q2a")
tab <- df2 %>% select(all_of(c("Q2.2", 
                                "missingness_Q2a"))) %>% 
                  table(useNA = 'ifany')
tab %>% create_pdf_table(caption = 
                "Cross-tabulation of Beliefs2 and Q2 answer",
                    row_names = TRUE, label = TRUE)


# data[["Q1a"]]
```


### Check Values 

```{r descriptive}
# the age column 
columns_to_summarize <-  c("QID30")  # Replace with your column names
summarize_statistics(data, columns_to_summarize) %>% 
             create_pdf_table(caption = "Descriptive Stats of Age")
```


```{r furthercheck}
# check both missingness and values 
# rename by column label
# risk_comprehension <- c("Q1.11", "Q2.11")
# risk_comp_label <- c("RComp1", "RComp2")

# object_num <- c("Q1.12", "Q2.12", "Q3.11")
# object_label <- c("ObjNum1", "ObjNum2", "ObjNum3")

df1 <- rename_columns_by_labels(data, risk_comprehension)

summarize_missingness(df1, risk_comp_label) %>% 
  create_pdf_table(caption = "Check Missingness: Risks Comprehension")

summarize_statistics(df1, "RComp1") %>% 
             create_pdf_table(caption = "Descriptive Stats of Risks Comprehension", font_size = 8)

summarize_statistics(df1, "RComp2") %>% 
             create_pdf_table(caption = "Descriptive Stats of Risks Comprehension", font_size = 8)


df2 <- rename_columns_by_labels(data, object_num)

summarize_missingness(df2, object_label) %>% 
  create_pdf_table(caption = "Check Missingness: ObjNums")

summarize_statistics(df2, "ObjNum1") %>% 
             create_pdf_table(caption = "Descriptive Stats of Obj Nums", font_size = 8)
summarize_statistics(df2, "ObjNum2") %>% 
             create_pdf_table(caption = "Descriptive Stats of Obj Nums", font_size = 8)
summarize_statistics(df2, "ObjNum3") %>% 
             create_pdf_table(caption = "Descriptive Stats of Obj Nums", font_size = 8)

```

