---
title: "RQ4 analysis"
author: "Risk Rejection Team: Guannan Shen"
date: last-modified
execute: 
  warning: false
  echo: false
format:
  html:
    toc: true
    toc-depth: 5
    toc-title: "Jump To"
    highlight-style: github
    code-line-numbers: true
    page-layout: article
    embed-resources: true
editor: source
---

```{r}
#| label: libraries
#| include: false

## set up workspace
rm(list = ls())
library(tidyverse)
library(magrittr)
library(gt)       # html table 
library(knitr)
library(gtsummary)

# helper functions
source("./basic.R")       # R functions definitely applicable to other projs
source("./helper.R")      # data wrangling, renaming functions for this proj
source("./data_clean_time.R")    # time cols related functions 
source("./table_helper.R")
source("./missing_helper.R")
source("./figure_helper.R")

```


```{r}
#| label: global_vars
#| include: false

source("./global_vars.R")

df <- readRDS("../data/processing/rs_pilot_rq4_dataset.rds") 

df_full <- readRDS("../data/processing/rs_pilot_rq4_nomissing_dataset.rds") 

# TODO:  Erika need more Crosstab 

```


# RQ4: inattentive responders

**How do different methods for identifying potential inattentive responders perform?**


## Indicators Breakdown

- Create Speeder flag (1 = non-speeder, 0 = speeder), according to 0.5 * median_duration.  (**FIX, 1 = pass, 0 = fail**)

- Create Attflag1 (1 = pass, 0 = fail for AttCheck1).  

- Create Attflag2 (1 = pass, 0 = fail for AttCheck2). 

- Create Attcount1 (sum of Attflag1 and Attflag2), count of passed attention checks (either 0, 1, or 2).  

- Create Attcount2 (sum of Attflag1, Attflag2, and Use_of_data), count of passed attention checks and the use of data flag (0 to 3).

- Create Attcount3, the sum (0-4) of people who pass the Speeder, Attflag1, Attflag2, and Use_of_data variables, where “pass” for Speeder is non-speeders. 

- Create Attcount4, (0-3) Sum of passed data use questions, speed, and **passed at least one of the two attention checks**. 



```{r}
#| label: rs4_prep
#| 
att <- c("Speeder", "Attflag1", "Attflag2", "Use_of_data")
att_count <- paste0("Attcount", 1:4)
cols <- c("Duration (in seconds)")

```

## Questions Breakdown

We want to see the frequencies (and %) for each of the 3 criteria:

1. How many are speeding?   
2. How many answer each of the directed questions incorrectly? And then a count of how many they answered correct/incorrect (0/1/2).    
3. How many answer the self-reported “in your honest opinion” that we should not use their data.  
4. Between speeders, “don’t use my data” (Q8 Use of data), and incorrectly answered 2/2 directed questions. Please provide frequencies and % for all.  
5. Also compute how many people miss at least 1 of the 3 criteria, and a frequency (and %) of how many people miss 0 vs 1 vs 2 vs 3 criteria

6. Is use of data related to the number of attention checks missed? (cross-tabs of attcount1 and use-of-data )

7. Correlations among speeding, use of data and the number of attention checks missed (Three-way cross tables Speeder VS. Attcount1 by Use_of_data).

# Frequency Tables

## Single frequency tables with Missing as Fails

```{r}
#| label: rq4_single_table2
df_full %>% tbl_summary(
      include = c(att, att_count),
      statistic = list(all_categorical() ~ "{n} ({p}%)"),
    digits = all_continuous() ~ 2,
    missing_text = "(Missing)",
      label = list(
                Attflag1 ~ "Attflag1: Attention Check Q1",
                Attflag2 ~ "Attflag2: Attention Check Q2",
                Attcount1 ~ "Attcount1: Attflag1 + Attflag2",
    Attcount2 ~ "Attcount2: Attflag1 + Attflag2 + Use_of_data",
    Attcount4 ~ "Attcount4: Pass_atleast1_check + Speeder + Use_of_data",
    Attcount3 ~ "Attcount3: Attflag1 + Attflag2 + Use_of_data + Speeder")
  ) %>% add_n()  %>% 
  bold_labels() %>% 
  modify_header(label ~ "**Characteristics**")

```



## Cross frequency tables with Missings as Fails

```{r}
#| label: crosstable2a

####### No Missing #############
tbl_cross(
  data = df_full,
  row = Speeder,       
  col = Use_of_data,  
  missing_text = "Missing",
  percent = "cell"       # Display counts and percentages
) %>%
  add_p() %>% bold_labels() 

tbl_cross(
  data = df_full,
  row = Speeder,       
  col = Attcount1,  
  missing_text = "Missing",
  percent = "cell"       # Display counts and percentages
) %>%
  add_p() %>% bold_labels() %>% 
  modify_spanning_header(all_stat_cols() ~ "**Attcount1: Attflag1 + Attflag2**")

tbl_cross(
  data = df_full,
  row = Speeder,       
  col = Attcount2,  
  missing_text = "Missing",
  percent = "cell"       # Display counts and percentages
) %>%
  add_p() %>% bold_labels() %>% 
  modify_spanning_header(all_stat_cols() ~ "**Attcount2: Attflag1 + Attflag2 + Use_of_data**")

tbl_cross(
  data = df_full,
  row = Speeder,       
  col = Attcount3,   
  missing_text = "Missing",
  percent = "cell"       # Display counts and percentages
) %>%
  add_p() %>% bold_labels() %>% 
  modify_spanning_header(all_stat_cols() ~ "**Attcount3: Attflag1 + Attflag2 + Use_of_data + Speeder**")

tbl_cross(
  data = df_full,
  row = Speeder,       
  col = Attcount4,   
  missing_text = "Missing",
  percent = "cell"       # Display counts and percentages
) %>%
  add_p() %>% bold_labels() %>% 
  modify_spanning_header(all_stat_cols() ~ "**Attcount4: Pass_atleast1_check + Speeder + Use_of_data**")

tbl_cross(
  data = df_full,
  row = Use_of_data,       
  col = Attcount1,  
  missing_text = "Missing",
  percent = "cell"       # Display counts and percentages
) %>%
  add_p() %>% bold_labels() %>% 
  modify_spanning_header(all_stat_cols() ~ "**Attcount1: Attflag1 + Attflag2**")
```

## Three-way cross tables Speeder VS. Attcount1 by Use_of_data

```{r}
#| label: crosstable2b

df_full %>%
  select(Use_of_data, Attcount1, Speeder) %>%
  tbl_strata(
    strata = Use_of_data,
    .tbl_fun =
      ~ .x %>%
      tbl_cross(row = Speeder,       
  col = Attcount1,  
  missing_text = "Missing",
  percent = "cell") %>%
  add_p() %>% bold_labels()  %>% 
  modify_spanning_header(all_stat_cols() ~ "Attcount1: Attflag1 + Attflag2")
  )

```

## Dataset with missing values (for reference)

### Single tables with Missing

```{r}
#| label: rq4_single_table1

# att <- c("Speeder", "Attflag1", "Attflag2", "Use_of_data")
# att_count <- paste0("Attcount", 1:3)

df %>% tbl_summary(
      include = c(att, att_count),
      statistic = list(all_categorical() ~ "{n} ({p}%)"),
    digits = all_continuous() ~ 2,
    missing_text = "(Missing)",
      label = list(
                Attflag1 ~ "Attflag1: Attention Check Q1",
                Attflag2 ~ "Attflag2: Attention Check Q2",
                Attcount1 ~ "Attcount1: Attflag1 + Attflag2",
    Attcount2 ~ "Attcount2: Attflag1 + Attflag2 + Use_of_data",
    Attcount4 ~ "Attcount4: Pass_atleast1_check + Speeder + Use_of_data",
    Attcount3 ~ "Attcount3: Attflag1 + Attflag2 + Use_of_data + Speeder")
  ) %>% add_n()  %>% 
  bold_labels() %>% 
  modify_header(label ~ "**Characteristics**")
```



### Cross tables with Missings

```{r}
#| label: crosstable1a

# rs4_vars <- c("Use_of_data", "Speeder", "Attflag1", 
#              "Attflag2", "Attcount1", "Attcount2", "Attcount3")

####### Has Missing #############
tbl_cross(
  data = df,
  row = Speeder,       
  col = Use_of_data,  
  missing_text = "Missing",
  percent = "cell"       # Display counts and percentages
) %>%
  add_p() %>% bold_labels() 

tbl_cross(
  data = df,
  row = Speeder,       
  col = Attcount1,  
  missing_text = "Missing",
  percent = "cell"       # Display counts and percentages
) %>%
  add_p() %>% bold_labels() %>% 
  modify_spanning_header(all_stat_cols() ~ "**Attcount1: Attflag1 + Attflag2**")

tbl_cross(
  data = df,
  row = Speeder,       
  col = Attcount2,  
  missing_text = "Missing",
  percent = "cell"       # Display counts and percentages
) %>%
  add_p() %>% bold_labels() %>% 
  modify_spanning_header(all_stat_cols() ~ "**Attcount2: Attflag1 + Attflag2 + Use_of_data**")

tbl_cross(
  data = df,
  row = Speeder,       
  col = Attcount3,   
  missing_text = "Missing",
  percent = "cell"       # Display counts and percentages
) %>%
  add_p() %>% bold_labels() %>% 
  modify_spanning_header(all_stat_cols() ~ "**Attcount3: Attflag1 + Attflag2 + Use_of_data + Speeder**")

tbl_cross(
  data = df,
  row = Speeder,       
  col = Attcount4,   
  missing_text = "Missing",
  percent = "cell"       # Display counts and percentages
) %>%
  add_p() %>% bold_labels() %>% 
  modify_spanning_header(all_stat_cols() ~ "**Attcount4: Pass_atleast1_check + Speeder + Use_of_data**")

tbl_cross(
  data = df,
  row = Use_of_data,       
  col = Attcount1,  
  missing_text = "Missing",
  percent = "cell"       # Display counts and percentages
) %>%
  add_p() %>% bold_labels() %>% 
  modify_spanning_header(all_stat_cols() ~ "**Attcount1: Attflag1 + Attflag2**")
```



### Three-way cross tables Speeder VS. Attcount1 by Use_of_data (with missing)

```{r}
#| label: crosstable1b

df %>%
  select(Use_of_data, Attcount1, Speeder) %>%
  tbl_strata(
    strata = Use_of_data,
    .tbl_fun =
      ~ .x %>%
      tbl_cross(row = Speeder,       
  col = Attcount1,  
  missing_text = "Missing",
  percent = "cell") %>%
  add_p() %>% bold_labels()  %>% 
  modify_spanning_header(all_stat_cols() ~ "Attcount1: Attflag1 + Attflag2")
  )

```




```{r}
#| label: test1

```

