---
title: "RS Pilot Trust Measures and Risk Skepticism Outcomes"
author: "Risk Rejection Team: Guannan Shen"
date: last-modified
execute: 
  warning: false
  echo: false
format:
  html:
    toc: true
    toc-depth: 5
    toc-title: "Jump To"
    highlight-style: github
    code-line-numbers: true
    page-layout: article
    embed-resources: true
editor: source
---

```{r}
#| label: libraries
#| include: false

## set up workspace
rm(list = ls())
library(tidyverse)
library(magrittr)
library(gt)       # html table 
library(knitr)
library(gtsummary)

library(questionr)
library(readxl)

# helper functions
source("./basic.R")       # R functions definitely applicable to other projs
source("./helper.R")      # data wrangling, renaming functions for this proj
source("./data_clean_time.R")    # time cols related functions 
source("./table_helper.R")
source("./missing_helper.R")
source("./figure_helper.R")

```


```{r}
#| label: global_vars
#| include: false

source("./global_vars.R")

# 3_rs_pilot_data_riskrejection.R
df <- readRDS("../data/processing/rs_pilot_risk_rejection_modified_dataset.rds") 

# trust questions/labels
df_trust <- read_excel("../data/processing/trust_measures.xlsx")

# trust_subscales <- c("GroupMed_Suspicion", "GroupMed_Disparities",
#                      "HealthSys_Competence", "HealthSys_Values")

# correlations between trust measures and rs outcomes
# rs_outcomes <- c("Abs_RReject_diff", "RReject_diff", 
#                 "RReject_mean", "RReject_comp_3")

df <- df %>%
  mutate(RReject_comp_3_numeric = case_when(
    RReject_comp_3 == "underestimate" ~ 1,
    RReject_comp_3 == "accurate estimate" ~ 2,
    RReject_comp_3 == "overestimate" ~ 3
  ))


```


# Correlations Between Trust Subscales and Risk Skepticism Outcomes


## Description of Predictors and Outcomes

### Predictors 

The Group-Based Medical Mistrust:

Subscales:

- GroupMedMis1 - GroupMedMis6: Suspicion, **GroupMed_Suspicion**.   
- GroupMedMis7 - GroupMedMis9: Group disparities in health care, **GroupMed_Disparities**.   

The Health Care System Distrust:   

Subscales:

- HealthSysDis1 - HealthSysDis4: Competence, **HealthSys_Competence**;     
- HealthSysDis5 - HealthSysDis9: Values, **HealthSys_Values**.  

### Outcomes 

Skepticism on the absolute scale (Absolute numeric risk skepticism):  

- (Absolute value of) Difference between RReject1 and breast cancer risk estimates (abs_risk_rounded)   
- **RReject_diff**, **Abs_RReject_diff**   
- Key part of code "RReject_diff = RReject1 - abs_risk_rounded" and "Abs_RReject_diff = abs(RReject_diff)". 


Skepticism on the comparative scale (Comparative risk skepticism):  

- Combination of RReject3 and Abs_risk_relative_risk   
- 3 categories outcome, **RReject_comp_3**, underestimate, accurate estimate, overestimate.  


Skepticism on the likert “belief” scale (Disbelief risk skepticism), **RReject_mean**:

- Average of RReject4 - RReject7 (1 - 5, 5 = Disagree a lot.)  

- Key part of code, "RReject_mean = rowMeans(across(all_of(paste0("RReject", 4:7))))"


## Correlations Between Trust Subscales and RS Outcomes

To calculate correlations:    

- **RReject_comp_3**, underestimate, accurate estimate, overestimate transformed to **RReject_comp_3_numeric** as 1, 2, 3.  

- Using **Pearson** correlation between Trust subscales and RReject_diff, Abs_RReject_diff, and RReject_mean, Using **Spearman rank** correlation between Trust subscales and RReject_comp_3_numeric.   


### All Subjects

```{r}
#| label: cor1

# cor
# cor.test

# cor(df$GroupMed_Suspicion, df$RReject_comp_3_numeric, 
#     use = "pairwise.complete.obs", method = "spearman")
# 
# cor(df$GroupMed_Suspicion, df$RReject_diff, 
#     use = "pairwise.complete.obs", method = "pearson")


# Define trust subscales and risk skepticism outcomes
trust_subscales <- c("GroupMed_Suspicion", "GroupMed_Disparities", 
                     "HealthSys_Competence", "HealthSys_Values")
rs_outcomes <- c("Abs_RReject_diff", "RReject_diff", 
                 "RReject_mean", "RReject_comp_3_numeric")

# Function to calculate correlation
calculate_correlation <- function(x, y, method) {
  cor(x, y, use = "pairwise.complete.obs", method = method)
}

# Create an empty matrix to store the results
correlation_matrix <- matrix(NA, nrow = length(rs_outcomes), 
                             ncol = length(trust_subscales),
                             dimnames = list(rs_outcomes, trust_subscales))

# Calculate Pearson correlations for the first three outcomes
for (outcome in rs_outcomes[1:3]) {
  for (subscale in trust_subscales) {
    correlation_matrix[outcome, subscale] <- calculate_correlation(
      df[[outcome]], df[[subscale]], method = "pearson"
    )
  }
}

# Calculate Spearman correlation for RReject_comp_3_numeric
for (subscale in trust_subscales) {
  correlation_matrix["RReject_comp_3_numeric", 
                     subscale] <- calculate_correlation(
    df[["RReject_comp_3_numeric"]], df[[subscale]], method = "spearman"
  )
}

# Convert the matrix to a data frame and round the values
correlation_df <- as.data.frame(correlation_matrix) %>%
  mutate_all(~ round(., 4))

# Display the correlation table
correlation_df %>%
  kable(caption = 
          "Correlation Table: Trust Subscales and Risk Skepticism Outcomes")

```
### Race Subgroups

```{r}
#| label: cor2

# Function to calculate correlations and store in a data frame
calculate_correlations_by_race <- function(race_group) {
  # Filter the data for the current race group
  race_data <- df %>% filter(Race_Ethnicity == race_group)
  
  # Create an empty matrix to store the results
  correlation_matrix <- matrix(NA, nrow = length(rs_outcomes), 
                               ncol = length(trust_subscales),
                               dimnames = list(rs_outcomes, trust_subscales))
  
  # Calculate Pearson correlations for the first three outcomes
  for (outcome in rs_outcomes[1:3]) {
    for (subscale in trust_subscales) {
      correlation_matrix[outcome, subscale] <- cor(
        race_data[[outcome]], race_data[[subscale]], 
        use = "pairwise.complete.obs", method = "pearson"
      )
    }
  }
  
  # Calculate Spearman correlation for RReject_comp_3_numeric
  for (subscale in trust_subscales) {
    correlation_matrix["RReject_comp_3_numeric", subscale] <- cor(
      race_data[["RReject_comp_3_numeric"]], race_data[[subscale]], 
      use = "pairwise.complete.obs", method = "spearman"
    )
  }
  
  # Convert the matrix to a data frame and round the values
  correlation_df <- as.data.frame(correlation_matrix) %>%
    mutate_all(~ round(., 4))
  
  # Return the correlation table
  correlation_df
}

# Calculate correlations for each race group
correlations_white <- calculate_correlations_by_race("White")
correlations_black <- calculate_correlations_by_race("African or African American / Black")

# Display the correlation tables
correlations_white %>%
  kable(caption = "Correlation Table for White Subjects: Trust Subscales and Risk Skepticism Outcomes")

correlations_black %>%
  kable(caption = "Correlation Table for African or African American Subjects: Trust Subscales and Risk Skepticism Outcomes")

```



```{r}
#| label: test1


```


```{r}
#| label: test2

```



