---
title: "rs_pilot_rq1_tests"
author: "Risk Rejection Team: Guannan Shen"
date: last-modified
execute: 
  warning: false
  echo: false
format:
  html:
    toc: true
    toc-depth: 5
    toc-title: "Jump To"
    highlight-style: github
    code-line-numbers: true
    page-layout: article
    embed-resources: true
editor: source
---

```{r}
#| label: libraries
#| include: false

## set up workspace
rm(list = ls())
library(tidyverse)
library(magrittr)
library(gt)       # html table 
library(knitr)
library(gtsummary)
library(stargazer)
library(truncreg)
library(questionr)

# helper functions
source("./basic.R")       # R functions definitely applicable to other projs
source("./helper.R")      # data wrangling, renaming functions for this proj
source("./data_clean_time.R")    # time cols related functions 
source("./table_helper.R")
source("./missing_helper.R")
source("./figure_helper.R")

```


```{r}
#| label: global_vars
#| include: false

source("./global_vars.R")

# TODO: 
# TODO: may change dataset
# 3_rs_pilot_data_riskrejection.R
df <- readRDS("../data/processing/rs_pilot_risk_rejection_modified_dataset.rds") 

```



# Research Question 1
**The question: Does asking about people’s perceived risk of developing breast cancer prior to providing their risk estimate affect the likelihood of them expressing risk skepticism?**

Conduct an experiment with 3 conditions, randomly assigned in a 1:1:1 allocation: 

(a) Risk perceptions measured before participants viewed the Gail model risk questions vs. 

(b) Risk perceptions measured after participants viewed the Gail model risk questions but before they viewed the results vs. 

(c) Risk perceptions measured after participants viewed their risk results. 

Where **c** is the control group, and group **a, b, c** correspond to 1, 2, 3 in the Experimental condition variable.

## Demographics

```{r}
#| label: demo

# move to 
# df %<>%  mutate(
#     # Convert Experimental condition to factor with labels
#     Condition = factor(`Experimental condition`, 
#                        levels = c(1, 2, 3), 
#       labels = c("Condition a", "Condition b", "Control")),
#     # Ensure Age is numeric
#     Age = as.numeric(Age)
#   )

df %>%
  dplyr::select(RReject_diff_binary, all_of(risk_calcs)) %>%
   tbl_summary(by = RReject_diff_binary,
               statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"),
    digits = all_continuous() ~ 2,
    missing_text = "(Missing)"
  ) %>% add_n()  %>% 
  bold_labels() %>% 
  modify_caption("**Table 1. Subjects Characteristics**") %>%
  add_p(test = list(all_continuous() ~ "oneway.test", 
                    all_categorical() ~ "fisher.test",
                    Biopsy ~ "fisher.test",
                    Hyperplasia ~ "fisher.test",
                    PlaceofBirth ~ "fisher.test",
                    `Asian/AA` ~ "fisher.test")) %>% 
  add_overall() %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ 
                           "**RReject_diff groups**") %>%
  modify_header(label ~ "**Characteristics**")

# Experimental Condition` != 3
```


## Questions Breakdown

Does experimental condition predict 
a) numeric absolute risk skepticism;  (RReject_diff, which is RReject1 - abs_risk_rouned)

b) disbelief risk skepticism; (RReject_mean, mean of RReject4 - 7)

c) comparative risk skepticism;  (Categorical outcome combine RReject3 and Abs_risk_relative_risk, use 3 levels outcome)

d) percieved risk (numeric and comparative) (RReject1, RReject3)

## Simple Linear regression

### Results Summary

RReject4 - 7 (Reverse the order):

Old:

1 = Disagree a lot, 

2 = Disagree a little, 

3 = Neither agree nor disagree,

4 = Agree a little, 

5 = Agree a lot. 

**NEW**:

1 = Agree a lot, 

2 = Agree a little, 

3 = Neither agree nor disagree,

4 = Disagree a little, 

5 = Disagree a lot.



The following table shows the estimates of coefficients and corresponding standard errors. The F statistic is the overall test as the ANOVA test (**There is no significant correlation as shown below**). 

```{r}
#| label: regression1

# Fit linear models for each outcome
model_RReject1 <- lm(RReject1 ~ Condition, data = df)
# model_RReject3 <- lm(RReject3 ~ Condition, data = df)
model_RR_diff <- lm(RReject_diff ~ Condition, data = df)
# model_RR_diff_abs <- lm(Abs_RReject_diff ~ Condition, data = df)
model_RReject_mean <- lm(RReject_mean ~ Condition, data = df)

summary(model_RReject1)
summary(model_RR_diff)
summary(model_RReject_mean)

# range(df$abs_risk_rounded)

# Summarize the three models
stargazer(model_RReject1, model_RR_diff, model_RReject_mean,
          type = "text",
          title = "Linear Regression Results for RReject1, RReject_diff, and RRejects Average",
          align = TRUE,
          single.row = TRUE)

```


### Diagnostic Plot

Diagnostic Plots for RReject1, RReject_diff, and RRejects Average respectively. 

```{r}
#| label: regression2

# Diagnostic plots
par(mfrow = c(2, 2))
plot(model_RReject1)
plot(model_RR_diff)
plot(model_RReject_mean)

```



## Chi-square tests for RReject3, Comparative Risk Skepticism

Post hoc test of chi-square test of independece referring to "https://pmc.ncbi.nlm.nih.gov/articles/PMC5737889/". 

In the considered problem for all cells in a contingency table, they are correlated, where the Holm-Bonferroni method can be used.


```{r}
#| label: testRReject3

tbl_cross(
  data = df,
  row = RReject3,       
  col = Condition,        
  percent = "cell"       # Display counts and percentages
) %>%
  add_p() %>% bold_labels()

# table(df$RReject3, df$Condition)
chisq.test(df$RReject3, df$Condition)

temp <- chisq.residuals(table(df$RReject3, df$Condition), 
                        digits = 4, 
                std = FALSE, raw = FALSE)

# Store standardized residuals as a matrix
std_residuals <- matrix(
  c(-1.0617, 0.6088, 0.4841,
    -1.5243, -0.3069, 1.7714,
     2.7258, -0.1065, -2.5703),
  nrow = 3, byrow = TRUE,
  dimnames = list(
    c("higher than", "about the same as", "lower than"),
    c("Control", "Condition a", "Condition b")
  )
)

# Convert the matrix to a data frame and pivot to long format
residuals_df <- as.data.frame(std_residuals) %>%
  rownames_to_column(var = "RReject3") %>%
  pivot_longer(
    cols = -RReject3, 
    names_to = "Condition", 
    values_to = "Std_residual"
  ) %>%
  # Calculate two-tailed p-values for the z-scores
  mutate(
    p_value = round(2 * pnorm(-abs(Std_residual)), 4)
  ) %>%  # Adjust p-values using Holm's method
  mutate(
    adjusted_p_value = p.adjust(p_value, method = "holm")
  )

# View the result
print(residuals_df) %>% kable()


tbl_cross(
  data = df,
  row = RReject_comp_2,       
  col = Condition,        
  percent = "cell"       # Display counts and percentages
) %>%
  add_p(test = "fisher.test") %>% bold_labels()

fisher.test(df$RReject_comp_2, df$Condition)

tbl_cross(
  data = df,
  row = RReject_comp_3,       
  col = Condition,        
  percent = "cell"       # Display counts and percentages
) %>%
  add_p() %>% bold_labels()

chisq.test(df$RReject_comp_3, df$Condition)

```

## Sensitivity analyses to inform outlier decisions

Models with the full data, and set of models that excludes RReject_diff > 90, and a set of models on only those with RReject_diff > 90.

### Excludes RReject_diff > 90 (size = 500)

```{r}
#| label: regression3

df1 <- df %>% filter(RReject_diff < 90)

model_RReject1 <- lm(RReject1 ~ Condition, 
                     data = df1)
# model_RReject3 <- lm(RReject3 ~ Condition, data = df)
model_RR_diff <- lm(RReject_diff ~ Condition, 
                    data = df1)
# model_RR_diff_abs <- lm(Abs_RReject_diff ~ Condition, data = df)
model_RReject_mean <- lm(RReject_mean ~ Condition, 
                         data = df1)

summary(model_RReject1)
summary(model_RR_diff)
summary(model_RReject_mean)


# Summarize the three models
stargazer(model_RReject1, model_RR_diff, model_RReject_mean,
          type = "text",
          title = "Linear Regression Results for RReject1, RReject_diff, and RRejects Average (RReject_diff < 90)",
          align = TRUE,
          single.row = TRUE)

chisq.test(df1$RReject3, df1$Condition)

fisher.test(df1$RReject_comp_2, df1$Condition)

tbl_cross(
  data = df1,
  row = RReject3,       
  col = Condition,        
  percent = "cell"       # Display counts and percentages
) %>%
  add_p() %>% bold_labels()

tbl_cross(
  data = df1,
  row = RReject_comp_3,       
  col = Condition,        
  percent = "cell"       # Display counts and percentages
) %>%
  add_p() %>% bold_labels()

chisq.test(df1$RReject_comp_3, df1$Condition)



```

### Only with RReject_diff >= 90 (size = 27)


```{r}
#| label: regression4
df1 <- df %>% filter(RReject_diff >= 90)

model_RReject1 <- lm(RReject1 ~ Condition, 
                     data = df1)
# model_RReject3 <- lm(RReject3 ~ Condition, data = df)
model_RR_diff <- lm(RReject_diff ~ Condition, 
                    data = df1)
# model_RR_diff_abs <- lm(Abs_RReject_diff ~ Condition, data = df)
model_RReject_mean <- lm(RReject_mean ~ Condition, 
                         data = df1)

summary(model_RReject1)
summary(model_RR_diff)
summary(model_RReject_mean)


# Summarize the three models
stargazer(model_RReject1, model_RR_diff, model_RReject_mean,
          type = "text",
          title = "Linear Regression Results for RReject1, RReject_diff, and RRejects Average (RReject_diff < 90)",
          align = TRUE,
          single.row = TRUE)

fisher.test(df1$RReject3, df1$Condition)

fisher.test(df1$RReject_comp_2, df1$Condition)

tbl_cross(
  data = df1,
  row = RReject3,       
  col = Condition,        
  percent = "cell"       # Display counts and percentages
) %>%
  add_p() %>% bold_labels()

tbl_cross(
  data = df1,
  row = RReject_comp_3,       
  col = Condition,        
  percent = "cell"       # Display counts and percentages
) %>%
  add_p() %>% bold_labels()

fisher.test(df1$RReject_comp_3, df1$Condition)


```





